RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-27 discussion.tex
yes

What is relationship to a standard CMS with R/Python

@@

Our environment assumes a high level of trust between its users.
Access control for information security is deferred to the host
operating system and web server. This decision should be re-examined,
but more sophisticated approaches such as information flow analysis
are an active research area and many subtle problems remain
\cite{Moore:2011:SAF}. We are hopeful that providing a richer
environment for collaboration and information sharing may aid
the application of information security research.

>>>>

@@

Our environment assumes a high degree of trust between users.
Access control for information security is delegated to the host
operating system and web server. In practice, most operating
systems and web servers rely either on coarse permission models,
which tend to be ineffective, or on detailed access control
lists, which tend to be cumbersome and complicated. 
Information security in RCloud should be re-examined, but more
sophisticated approaches such as information flow analysis are
still an active research area, and many subtle problems remain
\cite{Moore:2011:SAF}. We are hopeful that having a richer
environment for collaboration and information sharing will encourage
practical applications for new approaches to information security
in visual analytics.

### 2014-03-27 introduction.tex
yes

Main requirement is to satisfy these two sets of users: R coders and
managers. They work differently and want different things. What should
the infrastructure look like so they both coexist in peace? If this is
such a fundamental problem, why have other tools not addressed it?
Discuss Shiny (maybe in the disc. section).

\begin{itemize}
\item Constant technology transfer. Experiments in notebooks developed
by analysts need to become accessible in the production environment,
making it easy to push new features, prototypes, etc.
\item Dashboarding. To support the above, there should be a mode in which non-experts
can operate the experiments without coding.
\item Version control as a primary concept in the repository. There
needs to be a way to control the visibility of prototypes as they are
being developed and tested.
\item Coexistence in the current data ecosystem. We perceive the
isolation of current exploratory visualization and data analysis
environments to be a serious threat to a wider adoption of modern
techniques.
\item Modern interactive technologies. current isolation
notwithstanding, we find there is business demand for interactive
visualization tools. The main challenge here is how to integrate
these technologies so data scientists and statisticians can target
them, \emph{and} business-facing users can use them.
%% Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
%% \item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agrawala design considerations for collaborative visual analytics.
\end{itemize}

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
systems for data analysis and is well-supported by
a complex ecosystem of compatible packages, software
tools and other resources.
%
Of importance to us, there are existing
packages for high performance computing in the cloud,
and for generating web graphics. % no, there aren't. we wrote those!

>>>>

Our main requirement is to satisfy these two sets of users: R coders and
managers. They work differently and want different things. What should
the infrastructure look like so they both coexist in peace? If this is
such a fundamental problem, why have other tools not addressed it?
Discuss Shiny (maybe in the disc. section).

\begin{itemize}
\item Constant technology transfer. Experiments in notebooks developed
by analysts need to become accessible in the production environment,
making it easy to push new features, prototypes, etc.
\item Dashboarding. To support the above, there should be a mode
in which non-experts can operate the experiments without coding.
This may require some accomodation in code written by analysts,
but our goal is to make that as simple as we can.
\item Version control as a primary concept in the repository. There
needs to be a way to control the visibility of prototypes as they
are developed and tested.
\item Coexistence in the current data ecosystem. The isolation of
today's exploratory visualization and data analysis environments is
a real obstacle to wider adoption of novel data analysis methods.
\item Modern interactive technologies. Current isolation notwithstanding,
there is demand for interactive visualization tools. In some respects,
the prevalence of data journalism has raised expectations very high.
The main challenge is how to integrate these technologies so data
scientists and statisticians can program in them, \emph{and} business-facing
workers can operate them.
%% Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
%% \item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agrawala design considerations for collaborative visual analytics.
\end{itemize}

% What is the scope of our solution?
Our investigation focuses on the R language \cite{RCoreTeam:2013:R}
for statistical computing and graphics. R is one of the most popular
data analysis systems and is well-supported by a complex ecosystem
of compatible packages, software tools and other resources.
%
Of importance to us, there are many existing R packages, including
packages for high performance computing in the cloud, domain specific
models,
and for generating web graphics. % no, there aren't. we wrote those!
% well, right about that

### 2014-03-27 relatedwork.tex
yes

Our work has been inspired by and benefited from other proposals
to improve data analysis environments and processes,
including RStudio \cite{RStudio:2013:SWA},
R packages such as Markdown \cite{Allaire:2014:MMR},
knitr \cite{Xie:2013:DDW}
and Shiny \cite{RStudio:2013:SWA},
and iPython notebooks \cite{Perez:2007:IAS}
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals, such as providing a comprehensive environment
for analysis and programming, with shareable documents on the web.

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management ("devops" \cite{Httermann:2012:DD}) is a trend in web services and related fields. There is certainly an economic
benefit to making it possible for data scientists to expend a little more
effort in creating experiments, to eliminate the need for a programming
team to recreate their results in production.

>>>>

Our work has been inspired by and benefited from other efforts
to improve data analysis environments and processes,
including RStudio \cite{RStudio:2013:SWA},
the R packages Markdown \cite{Allaire:2014:MMR},
knitr \cite{Xie:2013:DDW}
and Shiny \cite{RStudio:2013:SWA},
and iPython notebooks \cite{Perez:2007:IAS}
to name a few. RStudio aims at providing an integrated development environment
for R, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals, such as providing a comprehensive environment
for analysis and programming, and shareable documents on the web.

One overall goal is to reduce the gap between implementers and deployers
of technology in visual analytics. The fusion of development with production
operations in software release management ("devops" \cite{Httermann:2012:DD})
is a trend in web services and related fields. By making it possible
for data scientists to expend a little more effort in the process of
creating experiments, it may be possible to eliminate the need for
programming teams to recreate their results in production with
a concomitant penalty in time and expense.

### 2014-03-27 system.tex
yes

The internal computing infrastructure of organizations has changed
radically in the last fifteen years. The shift from large
servers toward scalable, lower-cost, distributed systems (``the cloud'')
led to a software ecosystem of processes distributed over a
network (often virtually defined) communicating via some
high-level protocol, usually HTTP.  HTTP is dominant because web
browsers and servers are ubiquitous and available in essentially
all hardware devices, from tiny sensors, to handheld devices and
laptops, to rack-mounted servers.

@@

>>>>

The internal computing infrastructure of organizations has changed
radically in the last fifteen years. The shift from large
servers toward scalable, lower-cost, distributed systems (``the cloud'')
led to a software ecosystem of processes distributed over a
network (often virtually defined) communicating via some
high-level protocol, usually HTTP.  HTTP is dominant because web
browsers and servers are ubiquitous and available in almost
all hardware devices, from tiny sensors, to handheld devices and
laptops, to rack-mounted servers.

@@

What is relationship to a standard CMS with R/Python
